DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-12 paper/core/results.tex
results review

Fig.\ref{fig:ta_chart} shows the scheduling performance of different scheduling methods at different input sizes. The proposed network shows almost the same average turnaround time as HEFT algorithm for the seen data during training. However, for unseen data, the network shows slightly more poor performance than HEFT, but still better than that of genetic algorithms.

These results refer to the network ability to learn a good representation to the input machines and scheduling problem. The network performance degrades with high input sizes, as it's approximating HEFT, which is basically a greedy algorithm and prone to failure at complex situations. Genetic algorithms shows similar behaviour too, due to large population size.

\subsection{Execution Time}
\begin{table}
  \caption{Time comparison between the three discussed schedulers at different input sizes. Time measured in seconds.}
  \label{tab:exec_time}
  \centering
  \begin{tabular}{l l l l}
    \toprule
    Input Size & HEFT & GA & NN \\
    \midrule
    486	& 31.5 & 67.5 & 0.125 \\
    10000 & 305.5 & 602.5 & 0.125 \\
    84654 & 670.0 & 3967.0 & 0.125 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

We can see that the network consumes constant time in inference with different input sizes. This is because the network is trained on the maximum input length. However, HEFT and genetic algorithms execution time increases with input size. GA time increases more rapidly than HEFT, as it's a recursive optimization method but HEFT is a greedy-based method.

@@

However, this comes with a drawback of static scenarios. The neural network is trained with fixed input size, which is the maximum number of tasks, in our case. At inference time, the input to the network can't exceed that number. So, we have to define the maximum number of tasks to be scheduled, as well as the maximum number of resources. Moreover, the scheduling scenario for the proposed network should be static, where all available tasks should be known before the scheduler starts.

This gives neural networks a great potential to be a good task scheduler in static scenarios, where the maximum number of tasks and resources are known. However, in other dynamic scenarios, neural networks might not help much.

>>>>

Fig.\ref{fig:ta_chart} shows the scheduling performance of different scheduling methods at different input sizes. The proposed network shows almost the same average turnaround time as HEFT algorithm for the seen data during training. This is an indicator that the network can learn the underlying representation of the scheduling problem. However, this isn't enough, as the network needs to be tested on unseen data, too. For unseen data, the network shows slightly worse performance than HEFT, but still better than that of genetic algorithms. This indicates the ability of the network to generalize well to other inputs, as long as the network is provided by the same static scenarios and the same maximum number of tasks and resources. \\

These results refer to the network ability to learn a good representation to the input machines and scheduling problem. The network performance degrades with high input sizes, as it's approximating HEFT, which is basically a greedy algorithm and prone to failure at complex situations and large number of input tasks. Genetic algorithms shows similar behaviour too, due to large population size.

\subsection{Execution Time}
\begin{table}
  \caption{Time comparison between the three discussed schedulers at different input sizes. Time is measured in seconds.}
  \label{tab:exec_time}
  \centering
  \begin{tabular}{l l l l}
    \toprule
    Input Size & HEFT & GA & NN \\
    \midrule
    486	& 31.5 & 67.5 & 0.125 \\
    10000 & 305.5 & 602.5 & 0.125 \\
    84654 & 670.0 & 3967.0 & 0.125 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

We can see that the network consumes constant time in inference with different input sizes. This is because the network is trained on the maximum input length. However, HEFT and genetic algorithms execution time increases with input size. GA time increases more rapidly than HEFT, as it's a recursive optimization method but HEFT is a greedy-based method. The performance and static execution time of the network in inference make the network very useful in the situations where static scheduling environment is provided.

@@

However, this comes with a drawback of static scenarios. The neural network is trained with fixed input size, which is the maximum number of tasks and resources, in our case. At inference time, the input to the network can't exceed that number. So, we have to define the maximum number of tasks to be scheduled, as well as the maximum number of resources. Moreover, the scheduling scenario for the proposed network should be static, where all available tasks should be known before the scheduler starts.

This gives neural networks a great potential to be a good task scheduler in static scenarios, where the maximum number of tasks and resources are known. The network can be trained offline and then deployed to perform task scheduling. However, in other dynamic scenarios, neural networks might not help much.
